---
title: "lecture-notes"
author: "Souta Saechao"
date: "11/30/2021"
output: html_document
---
## Concept

Exploration of population dynamic patterns at **The Portal Project**.
How do counts of rodents like *Dipodomys* species change through time?

In this document I will:

1. Load data from the [Portal Project Teaching Database](http://figshare.com/articles/Portal_Project_Teaching_Database/1314459)
2. Process it into population time series
3. And make initial visualizations



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



# chunks

# Big
## smaller
### more smaller

# insert R (Ctrl+Alt+l)
<<<<<<< HEAD
## adding message=FALSE cleans up Doc 

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

## Data

```{r, cache=TRUE}
data <- read.csv("https://ndownloader.figshare.com/files/2292172")
head(data)
```

The data includes `r length(unique(data$species_id))` species.

## Analysis

Get the time-series of counts for all species.

```{r, message=FALSE, echo=FALSE, cache=TRUE}
time_series <-
  data %>%
  group_by(species_id, year) %>%
  summarize(count = n()) %>%
  filter(species_id %in% c('DM', 'DO', 'DS')) %>%
  na.omit()

knitr::kable(head(time_series))
```
=======
>>>>>>> 2fffd66b33b68e4b5eda49d5c4459d2c4e53d81a

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

## Data

<<<<<<< HEAD
```{r setup, include = FALSE}
=======
```{r}
data <- read.csv("https://ndownloader.figshare.com/files/2292172")
head(data)
```
>>>>>>> 2fffd66b33b68e4b5eda49d5c4459d2c4e53d81a


smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

```{r, echo=FALSE}
knitr::kable(
  mtcars[1:5, ], 
  caption = "A knitr kable."
)
```





